#  Problem 3

a. 
```{r}
set.seed(4)
rand_ts <- rnorm(1000)
acf(rand_ts, plot = FALSE)
```
+ Overall, this is true, but there is one outlier autocorrelation at 0.
+ This makes sense because a series will always be perfectly correlated with 
itself.

b. 
```{r}
acf(rand_ts, plot = TRUE)
```

+ Other than the lag line located at 0, yes, it appears that there is one 
autocorrelation at 10 that is significantly different from zero in the plot. 
There is another autocorrelation located at 22 that is just barely touching the 
dotted blue line, which may or may not be statistically significant.
+ Yes, this makes sense because with a normal distribution, there is a 95% 
chance that the normal distribution will fall within 2 standard deviations of
the mean, and therefore, a 5% chance that it will not (leading to a lag line
that crosses the blue dotted line). Here, we see 30 different lags represented.
Out of the 30 lags, we would assume that an average of 1.5 would show a 
statistically significan correlation, meaning that having one to two lag lines
crossing the blue line should be expected.
