
c. *(10 points)  Create two autocorrelation plots of the `trips_per_day_usertype` time series:  One for subscribers, and one for customers. First, we create the two autocorrelation time series.*

```{r, warning = FALSE, message = FALSE}
bike_customer_acf <- acf(filter(trips_per_day_usertype,
                               usertype == "Customer")$n_trips,
                        plot = FALSE)
bike_subsciber_acf <- acf(filter(trips_per_day_usertype,
                                usertype == "Subscriber")$n_trips,
                         plot = FALSE)
```

*And then we generate the both of them using ggplot. Here below we only generate the plot for the customer auto correlation function.*

```{r}
bike_customer_acf_df <- with(bike_customer_acf, data.frame(lag, acf))
ggplot(bike_customer_acf_df, aes(x = lag, y = acf)) + geom_col() +
  labs(title = "Autocorrelation of trips per day for Citi bike customers",
       x = "Lag (in days)",
       y = "Autocorrelation",
       caption = "Source: NYC Citi bike data")
```

*Generate the autocorrelation plot for the subscribers as well.*

```{r}
bike_subscriber_acf_df <- with(bike_subsciber_acf, data.frame(lag, acf))
ggplot(bike_subscriber_acf_df, aes(x = lag, y = acf)) + geom_col() +
  labs(title = "Autocorrelation of trips per day for Citi bike subscribers",
       x = "Lag (in days)",
       y = "Autocorrelation",
       caption = "Source: NYC Citi bike data")
```

*Add to **both** plots*:

+ *An appropriate title*
+ *An appropriate source*
+ *Appropriate axis labels*

*In both time series, you should see that the ACF has its greatest peak at `lag=7`. How do you interpret this, considering that we computed the ACFs on daily-level data? Does it make sense, given the context of the data (number of rental bike trips per day)?*

This means that the ACF has its greatest peak 7 days (or 1 week) from the 
baseline. In other words, the number of rental bike trips per day for customers 
and subscribers is most correlated with itself at this point. This makes sense
considering weekly patterns in bike usage.
